---
title: "WUP_04"
author: "Robert Solis!"
date: "6/12/23"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
thedata<-read.csv(file="GSScsv.csv")



```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Mention that you intend to use chatGPT to the greatest extent possible. Give credit to chatGPT when you use it to create code in your report. Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

we wanted to find out by looking at the data we had. We copied write up 3 to read data in and changed the charcter variables into factor variables and saw that we had a numerical data which was wordsum and now we have a factor variable called degree.


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
ggplot(thedata, aes(x = DEGREE, y = WORDSUM)) +
geom_boxplot(fill = "skyblue", color = "darkblue", outlier.shape = NA) +
theme_minimal() +
labs(x = "DEGREE", y = "WORDSUM") +
theme(plot.title = element_text(hjust = 0.5)) +
ggtitle("Fancy Box Plot")

```

Lt High school would not overlap with junior College or Graduate, thus showing that it is very likely to be different schooling. In addition, graduate does not overlap with Highschool.Therefore, it also is likely to be different.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=thedata)
```
The average score on the WORDSUM test for graduates was a little over 10.Theirs a differcne between the average score in graduate school and the average score in Junior college. Further proving that the schools have difference from one another.

## Inferential Results

```{r}
# Perform one-way ANOVA
model <- aov(WORDSUM ~ DEGREE, data = thedata)

# Conduct post-hoc test (Tukey's HSD)
posthoc <- TukeyHSD(model)

# Print the results
print(posthoc)


```

```{r}
# Assuming you have the "thedata" data frame with "DEGREE" and "WORDSUM" columns

# Load the emmeans package
library(emmeans)

# Perform one-way ANOVA
result <- aov(WORDSUM ~ DEGREE, data = thedata)

# Perform Scheffe's post hoc test
comparison <- emmeans(result, pairwise ~ DEGREE, adjust = "scheffe")

# Print the comparison table
print(comparison)

```



<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfy the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In the graphical chart Lt High school doesn't overlap with junior College or Graduate. How ever the difference between the High schools is slight in graduation. And comparedly to the Colleges they seem not at all.
